Untitled

### 2022-12-13 draft1_Rcode.Rmd
Updating Q5 so that sampling does not have to select a certain number from each group

@@

```{r}
## Question 5 extra stuff

>>>>

#Need to edit as in bootstrapping dont care aout having same number in each group! (I think)

@@

```{r}
#Bootstrap where number in each group not set

bootFStat <- function(group,y,w,bootCount){
  #object to store B bootstrap estimates of f statistic
  Fstat.boot.est <- NULL
  #grouping values into dataset 
  data <- data.frame("group"=group,"Obs"=y,"weight"=w)
  #Adding id column so can sample by id to retain all info of row (obs and weight)
  data$id <- seq(1,dim(data)[1])

  for (b in 1:bootCount){
    #object to store value of y tilde * N 
    y.tilde.N <- 0

    #sampling dataset
    sample.id <- sample(data$id, size = length(y), replace = TRUE)
    #extracting weight and y value corresponding to id sampled
    sample.obs <- NULL
    sample.weight <- NULL
    sample.group <- NULL

    for (i in 1:length(y)){
      sample.obs[i] <- data$Obs[data$id == sample.id[i]]
      sample.weight[i] <- data$weight[data$id == sample.id[i]]
      sample.group[i] <- data$group[data$id == sample.id[i]]
    }
    #creating dataset of sample
    sample.dataset <- data.frame("group"=sample.group,"Obs"=sample.obs,"weight"=sample.weight)

    #computing statistics to calculate f-stat
    for (group_val in unique(sample.dataset$group)){
      group.dataset <- data.frame("Obs"=sample.dataset$Obs[sample.dataset==group_val],
                                  "weight"=sample.dataset$weight[sample.dataset==group_val])

      #calculating number of obs for current group
      assign(paste0("nobs.",group_val),dim(group.dataset)[1])

      #Calculating y tilde_{i} for current group
      y.tilde.group <- sum(group.dataset$Obs*group.dataset$weight)/dim(group.dataset)[1]
      assign(paste0("y.tilde.",group_val),y.tilde.group)

      #updating y tilde using current group
      y.tilde.N <- y.tilde.N + sum(group.dataset$Obs*group.dataset$weight)

      #Calculating part of denominator of f-statistic corresponding to current group
      f.denom.group.part <- sum((group.dataset$Obs*group.dataset$weight-y.tilde.group)^2)
      assign(paste0("f.denom.",group_val),f.denom.group.part)

    }
    #calculating y tilde
    y.tilde <- y.tilde.N/length(y)

    #calculating summation parts of numerator and denominator of f statistic
    fstat.num <- 0
    fstat.denom <- 0
    for (group_val in unique(data$group)){
      fstat.num <- fstat.num+get(paste0("nobs.",group_val))*(get(paste0("y.tilde.",group_val))-y.tilde)^2
      fstat.denom <- fstat.denom + get(paste0("f.denom.",group_val))
    }
    #calculating F stat
    fstat <- (fstat.num/(length(unique(group))-1))/(fstat.denom/(length(y)-length(unique(group))))
    Fstat.boot.est[b] <- fstat

  }
  #Calculating standard error of bootstrap f statistic
  bootstr.mu <- sum(Fstat.boot.est)/length(Fstat.boot.est)
  bootstr.se <- sqrt(sum((Fstat.boot.est-bootstr.mu )^2)/(length(Fstat.boot.est-1)))

#b
set.seed(2022)
bootFStat(eco.df$habitat,eco.df$density,eco.df$weight,1000)  
```

```{r}
## Question 5 extra stuff (use this to check results by doing piece by piece)
